State of the Practice for Lattice Boltzmann Method Software

### 2022-04-23 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
reviewed Section 12

This paper will help scientists select a suitable LBM package for their needs.
However, its more fundamental purpose is to deepen our understanding of the
state of the practice for developing LBM software. Understanding what artifacts
are produced, what tools are used, what process are employed and what pain
points are experienced, is the starting point for devising future methods and
tools for reducing development time and improving software quality.

To assess the state of the practice, we followed five steps:
\begin{inparaenum}[i)]
	\item Identified a list of 24 LBM packages;
	\item Measured the packages using a measurement template (the template
	consists of 108 questions to assess 9 qualities (including the qualities of
	installability, usability and visibility))
	\item Ranked the software using the Analytic Hierarchy Process (AHP);
	\item Interviewed developers (each interview consisted of 20 questions and took
	about an hour); and, 
	\item Conducted a domain analysis. 
\end{inparaenum}
The collected data was analyzed by: 
\begin{inparaenum}[i)]
	\item Comparing our ranking by best practices against the ranking by
	popularity;
	\item Comparing artifacts, tools, and processes to current research software
	development guidelines; and, 
	\item Exploring pain points.
\end{inparaenum}

@@

Our domain analysis (Section~\ref{SecDomainAnalysis}) was relatively shallow.  In
the future we would like to dig more deeply.  We would like to produce tables of
commonalities, variabilities, and parameters of variation for the family of LBM
solvers. We could follow the template from \citep{smith2008commonality}, or
adopt the analysis techniques from \citep{weiss1998commonality}.
\citet{SmithAndChen2004} and \citet{SmithMcCutchanAndCarette2017} provide
examples that could be followed for a commonality analysis of a family of mesh
generating software and a family of material models, respectively.

>>>>

This paper will help scientists select a suitable LBM package for their needs.
However, its more fundamental purpose is to deepen our understanding of the
state of the practice for developing LBM software. Understanding what artifacts
are produced, what tools are used, what processes are employed and what pain
points are experienced is the starting point for devising future methods and
tools for reducing development time and improving software quality.

To assess the state of the practice, we followed five steps:
\begin{inparaenum}[i)]
	\item Identified a list of 24 LBM packages;
	\item Measured the packages using a measurement template (the template
	consists of 108 questions to assess 9 qualities (including the qualities of
	installability, usability and visibility);
	\item Ranked the software using the Analytic Hierarchy Process (AHP);
	\item Interviewed developers (each interview consisted of 20 questions and took
	about an hour); and, 
	\item Conducted a domain analysis. 
\end{inparaenum}
The collected data was analyzed by: 
\begin{inparaenum}[i)]
	\item Comparing our ranking by best practices against the ranking by
	popularity;
	\item Comparing artifacts, tools, and processes to current research software
	development guidelines; and, 
	\item Exploring pain points.
\end{inparaenum}

@@

Our domain analysis (Section~\ref{SecDomainAnalysis}) was relatively shallow.  In
the future we would like to dig more deeply.  We would like to produce tables of
commonalities, variabilities, and parameters of variation for the family of LBM
solvers. We could follow the template from \citet{smith2008commonality}, or
adopt the analysis techniques from \citet{weiss1998commonality}.
\citet{SmithAndChen2004} and \citet{SmithMcCutchanAndCarette2017} provide
examples that could be followed for a commonality analysis of a family of mesh
generating software and a family of material models, respectively.
